Upper limits on CN from exocomets transiting $\beta$~Pictoris

### 2025-04-18 src/tex/ms.tex
language corrections

\documentclass{aa}  
\usepackage{rotating}
\usepackage{natbib}
\usepackage{amsmath}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
\usepackage{float}
\usepackage{placeins}

\newcommand{\angstrom}{\textup{\AA}}

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {The young (23 Myr) nearby (19.4 pc) star $\beta$~Pictoris hosts an edge-on debris disk with two gas giant exoplanets in orbit around it.
   %
   Many transient absorption features have been detected in the rotationally broadened stellar lines, which are thought to be the coma of infalling exocomets crossing the line of sight towards Earth.}
  % aims heading (mandatory)
   {In the Solar system, the molecule cynaogen (\ce{CN}) and its associated ionic species are one of the most detectable molecules in the coma and tails of comets.
   %
   We perform a search for cyanogen in the spectra of \bp{} to detect or put an upper limit on this molecule's presence in a young, highly active planetary system.}
  % methods heading (mandatory)
   {We divide twenty year's worth of \ac{harps} spectra into those with strong exocomet absorption features, and those with only stellar lines.
   %
   The high signal to noise stellar spectrum normalises out the stellar lines in the exocomet spectra, which are then shifted and stacked on the deepest exocomet absorption features to produce a high signal to noise exocomet spectrum, and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.}
  % results heading (mandatory)
   {We do not detect \ce{CN} in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, to be compared to the typical 10$^9$ - 10$^{10}$ cm$^{-2}$ expected from scaling of the values in the Solar System comets.}

@@

The formation and evolution of planets and their attendant moons is thought to occur in the first several million years of a planetary system.
%
Within our Solar system, comets deliver volatiles from the outermost reaches of the Oort cloud \citep{Obrien2018}, past the gas giants and terrestrial planets, even as close as a few solar radii.
%
It is therefore important to understand the distribution, nature and chemical composition of exocomets in other planet forming systems.

One of the closest young planetary systems is $\beta$~Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.
%
\bp{} is a young \citep[$\sim 25$ Myr; see ][ for discussions]{Lee24}, nearby \citep[$19.63\pm 0.06$ pc, ][]{Lindegren21} and early type star \citep[A6V; ][]{Gray06} which hosts an edge-on debris disk and at least two exoplanets, making it one of the most intensely studied young planetary systems.
%
The star is a rapid rotator \citep[$124\pm 3$\,\kms{}; ][]{Koen03} seen close to equator on.
%
Amongst these, the \ce{Ca} H and K lines show deep absorption down to 0.1 of the continuum level.
%
Deep within this rotationally broadened line there is a consistent and stable narrow absorption feature with a full width half maximum (FWHM) of a few km/s, attributed to the presence of the circumstellar material \citep{Hobbs85,VidalMadjar86}.

Transient absorption features appearing in the rotationally broadened Ca H and K features were proposed to be due to the transit of evaporating exocomets in front of the star \citep{Ferlet87}.
%
These features appear and disappear on the timescale of hours to days, with some features lasting up to tens of days and have red-shifted velocities from eighty kilometers per second, all the way down to (and merging with) the circumstellar line, with a few appearing on the blueward side \citep{LagrangeHenri92} with widths from a few up to tens of kilometers per second.
%
The absorption can be described by the transit of evaporating bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing calcium ions which are then seen as an additional absorption component \citep{Beust91}.
%
Intensive spectroscopic monitoring over several hours show both multiple components transiting the disk of the star \citep{Beust96} and changes of radial velocity of several components are consistent with Keplerian elliptical orbits \citep{Kennedy18} implying at least two \citep{Kiefer14,Pollard24} or more \citep{Heller24} distinct kinematic families of Beta Pictoris exocomets.
%
At least one event is derived with the orbit parallel to the rotational axis of the star \citep{Tobin19}.

From the multiple detections of exocomets in spectroscopy towards \bp{}, the broadband detection of exocomet tails transiting a star were predicted in \citet{1999A&A...343..916L}.
%
A chain of seven exocomets were proposed to explain the shape of one eclipse seen towards KIC~8462852 in \citet{Kiefer17}, and
single exocomet transits were subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.
%
Observations of \bp{} in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar system \citep{LecavelierdesEtangs22,Pavlenko22}.
%
Automated searches in photometry \citep{Kennedy19} and spectroscopy \citep{BendahanWest24} for additional exocomet systems have been met with limited success.

To the contrary of what is observed in the case of Beta Pictoris exocomets, most molecular and atomic signatures detected in the coma of Solar system comets are emission lines/bands instead of absorptions.
%
Spectroscopic observations of Solar system comets when they are very close to the Sun are rare due to observational difficulties.
%
The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
%
For this comet, it was noticed that the main emission bands/lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
%
At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum.
%
However, at 0.15~au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ion{[O]}{i}, \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
%
Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007} and Na and K were detected for comet C/2011 L4 \citep{Fulle13} at 0.46 au.

@@

For the majority of Solar system comets, their optical spectra are dominated by the reflected sunlight from dust grains in their comae, plus molecular and atomic emission lines \citep[e.g. ][]{hyland2019}.
%
Most of the neutral and ionic molecular emission results from resonance fluorescence with solar photons.
%
Some species, such as \ce{H2O+} and \ce{CO+} result from ionization of parent molecules (i.e. molecules released directly by the sublimation of nuclear ices), all other molecules observed at optical wavelengths are second generation species, often created via photodissociation of parent molecules or released by organic-rich grains in the coma.
%
Another process also observed in optical spectrum of comets is prompt atomic emission  ([\ion{O}{i}], [\ion{C}{i}], and [\ion{N}{i}]).
%
Those forbidden transitions are the result of atoms produced in an excited state by the photodissociation of parent molecules in the coma.

Of all cometary gas emission, the highest signal to noise normally occurs with the \ce{CN} (0-0) band at $\lambda\simeq 3880$\AA.
%
It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the comae of comets observed at relatively large distances from the Sun \citep[e.g. ][]{Bus1991,Fitzsimmons1996}.
%
The relative abundance in the coma of most comets of \ce{OH/CN}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas coma.
%
Historically, the \ce{CN} was believed to be created from photodissociation of \ce{HCN}, which is present in abundances of the order of 1\% relative to water in cometary ices.
%
High-spatial resolution sub-mm mapping of \ce{HCN} distributions supports a nuclear source in some comets \citep{Cordiner2014}.
%
However, it is now known that in many comets a substantial fraction of \ce{CN} is released from sub-micron dust grains in the inner coma of comets \citep[e.g. ][]{Fray2005}.

The \ce{C2} (0-0) band at $\lambda\simeq 5160$\AA{}\ may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
%
The \ce{OH} (0-0) band at $\lambda\simeq 3080$ \AA{}\ generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
%
Strong \ce{CO+} emission bands have also been observed in a number of comets \citep[the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$; ][]{Biver2018}.
%
However this is normally significantly weaker than the observed \ce{CN} emission, with detection in only less than 20 comets.
%
Given the ubiquitous signature of \ce{CN} emission in Solar system comets, we have embarked on an archival search for this species in the exocomets around \bp{}.
%
Detection of this species would provide a solid link between cometary bodies in our Solar system and the \bp{} system.

We detail the observations in Section~\ref{sec:data}, along with the correction for the echelle blaze function and normalization of the spectra to a continuum.
%
Our search for \ce{CN} relies on a cross correlation search with a theoretical absorption spectrum for the molecule in Section~\ref{sect:CNsearch}, and the discussion and interpretation is in Section~\ref{sec:discuss} with our conclusions in Section~\ref{sec:conclusion}.

@@

We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and March 2020.
%
Although these observations cover a large baseline, the time between visits varies between 1 day and $\sim$2.2 years.
%
Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.
%
This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labelling in the fits header -- corresponding to 3780\,\AA{} and 4075\,\AA) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
%
To avoid potential edge effects from order merging,  we used the E2DS files downloaded directly from the ESO archive for our analysis.

@@

After all the spectra were all transformed into the stellar rest frame, an average nightly spectrum was made from all spectra within a night for each of the nights of observations. This was done after correcting for variations in the effective blaze profile (e.g., due to instrumental changes, differential slit/fiber losses, atmospheric absorption, etc.), as outlined below. Note that after this correction, the data still have the overall instrumental blaze-profile included.

@@

The night of 2018-05-06, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.
%
The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
%
Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
%
This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin, clipping points more than 2.7 Median Absolute Deviations (MAD) away from the median of each bin.
%
This binned ratio was then fitted using a second order polynomial.
%
The original spectrum was finally divided by this polynomial to correct for the changes.

Note that the change of fiber for HARPS in June 2015 (JD$\sim$2,457,180) resulted in an overall change in the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in Sect.~\ref{sect:starcor}.

@@

After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
%
Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\,\AA{} - 4075\AA).

@@

The processing up to this stage removes most of the variations in the effective blaze function, but the overall stellar spectrum and, for HARPS, shape of the blaze profile, are still present and need to be removed.

We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.
%
This is done separately pre- and post-fiber change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.

After this post-processing the overall (residual) blaze profile and stellar spectrum still need to be removed.
%
Care must be taken to prevent the removal of (potential) narrow features from the circumstellar disk (as seen in e.g., the \ce{Fe} and \ion{Ca}{II} lines).
%
This is done by combining the nightly spectra without significant cometary activity (see Sect.~\ref{sect:FEBid}) and binning this stacked spectrum in wavelength in bins of 21 pixels.
%
Before binning, the spectrum in each bin was median absolute deviation (MAD) clipped to within $\pm$4.5 MAD of the median of the flux in the bin.
%
The clipped average of the fluxes within each bin was used.
%
Subsequently, the overall spectrum of the star and (residual) blaze was determined by cubic interpolation across the binned points, and divided out of the spectrum for each night.
%
As before, this was done separately pre- and post-fiber change.

@@

After the initial data analysis, we proceed to with our search for lines from \ce{CN}.
%
Although we are interested in lines from the exocomets, we first co-add the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar \ce{CN} absorption.
%
These coadded spectra are shown in Figure~\ref{fig:spec_CN_stellar_frame}.
%
No obvious feature from the \ce{CN} band jumps out, and we need to combine the signal from the lines within the \ce{CN} band to improve the detection limits.
%
Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the 36 epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.

@@

The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 \kms{}.
%
The deepest absorption feature in each observing night was selected, and the location and depth stored.
%
For the comet sample we selected features deeper than 60\% while spectra with features below 15\% were flagged as `low activity'.
%
The distribution of feature locations and depths is shown in Figure~\ref{fig:FEB_velocity}. The dates, velocities and depths of the selected exocomets can be found in Tab.~\ref{tab:FEB_data}

The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in Figure~\ref{fig:spec_CN_comet_frame}.
%
As with the circumstellar \ce{CN}, there are no obvious lines from \ce{CN} visible, and we will need to combine multiple lines to improve the signal-to-noise ratio, and see if there is any \ce{CN} present.

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_stellar.pdf}
        \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
        %
        The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_stellar_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
        \caption{Similar to Figure~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the comet. The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_comet_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

@@

To combine the signal from the many \ce{CN} lines, we cross-correlate the data for each night with a grid of model of \ce{CN}.
%
Cross-sections for \ce{CN} were obtained from ExoMol\footnote{\url{https://www.exomol.com}} \citep{Tennyson12,Tennyson16,Brooke14} with molecular energy levels assumed to be in thermal equilibrium, i.e.\ Boltzmann distributed.
%
We made models for a wide range of temperatures (T$=$\{10, 20, 30, 50, 100, 200, 300, 500, 1000, 2000, 3000\} K) and column densities\footnote{Note that technically, for optically thin lines, this assumes a filling factor $f=1$.
%
Since $f$ is unknown, we actually measure N$f$} (N=\{$10^{11} \ldots 10^{15}$\} cm$^{-2}$.
%
Each of the models was then convolved to include an effective velocity dispersion using a Gaussian for FWHM=\{2.9, 5, 10, 15, 20\} \kms{}.
%
A value of 2.9 \kms{} corresponds approximately to the instrumental resolution of HARPS.
%
The theoretical spectra of \ce{CN} for several different temperatures are shown in Figure~\ref{fig:CN_theory}.

When creating the CCFs, the region around the narrow, circumstellar \ion{Fe}{I} lines in this wavelength region (see Figs.~\ref{fig:spec_CN_stellar_frame}~and~\ref{fig:spec_CN_comet_frame}) were masked to avoid contamination, especially for the higher temperature CN models.
%
We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm0.35$\AA{} for the \ion{Fe}{I} 3859.9\AA{} line, while for the other lines a width of $\pm0.15$\AA{} was used.

Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf_mean}) do not show any clear signals, and we therefore proceed to estimate our detection limits.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/HARPS_CN_stellar_frame.pdf}
        \caption{\ce{CN} measurement limits in the stellar rest frame for a \ce{CN} line width of 2.7 \kms{}. Contours show signal to noise upper limits.}
        \label{fig:CN_stellar_frame}
        \script{plot_HARPS_CN_stellar_frame.py}
    \end{centering}
\end{figure}

>>>>

\documentclass{aa}  
\usepackage{rotating}
\usepackage{natbib}
\usepackage{amsmath}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
\usepackage{float}
\usepackage{placeins}
\newcommand{\angstrom}{\textup{\AA}}

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {The young (23 Myr) nearby (19.4 pc) star $\beta$~Pictoris hosts an edge-on debris disk with two gas giant exoplanets in orbit around it.
   %
   Many transient absorption features have been detected in the rotationally broadened stellar lines, which are thought to be the coma of infalling exocomets crossing the line of sight towards Earth.}
  % aims heading (mandatory)
   {In the Solar System, the molecule cynaogen (\ce{CN}) and its associated ionic species are one of the most detectable molecules in the coma and tails of comets.
   %
   We perform a search for cyanogen in the spectra of \bp{} to detect or put an upper limit on this molecule's presence in a young, highly active planetary system.}
  % methods heading (mandatory)
   {We divide twenty year's worth of \ac{harps} spectra into those with strong exocomet absorption features, and those with only stellar lines.
   %
   The high signal-to-noise stellar spectrum normalises out the stellar lines in the exocomet spectra, which are then shifted and stacked on the deepest exocomet absorption features to produce a high signal-to-noise exocomet spectrum, and search for the \ce{CN} band head using a model temperature dependent cross-correlation template.}
  % results heading (mandatory)
   {We do not detect \ce{CN} in our data, and place a temperature and broadening dependent 5$\sigma$ upper limit between 10$^{12}$\,cm$^{-2}$ and 10$^{13}$\,cm$^{-2}$, to be compared to the typical 10$^9$ - 10$^{10}$ cm$^{-2}$ expected from scaling of the values in the Solar System comets.}

@@

The formation and evolution of planets and their attendant moons is thought to occur in the first several million years of a planetary system.
%
Within our Solar System, comets deliver volatiles from the outermost reaches of the Oort cloud \citep{Obrien2018}, past the gas giants and terrestrial planets, even as close as a few solar radii.
%
It is therefore important to understand the distribution, nature and chemical composition of exocomets in other planet forming systems.

One of the closest young planetary systems is $\beta$~Pictoris, which has been studied intensively both with direct imaging and with spectroscopy.
%
\bp{} is a young \citep[$\sim 25$ Myr; see ][ for discussions]{Lee24}, nearby \citep[$19.63\pm 0.06$ pc, ][]{Lindegren21} and early type star \citep[A6V; ][]{Gray06} which hosts an edge-on debris disk and at least two exoplanets, making it one of the most intensely studied young planetary systems.
%
The star is a rapid rotator \citep[$124\pm 3$\,\kms{}; ][]{Koen03} seen close to equator on.
%
Amongst these, the \ce{Ca} H and K lines show deep absorption down to 0.1 of the continuum level.
%
Deep within this rotationally broadened line there is a consistent and stable narrow absorption feature with a full width half maximum (FWHM) of a few \kms{}, attributed to the presence of the circumstellar material \citep{Hobbs85,VidalMadjar86}.

Transient absorption features appearing in the rotationally broadened \ce{Ca} H and K features were proposed to be due to the transit of evaporating exocomets in front of the star \citep{Ferlet87}.
%
These features appear and disappear on the timescale of hours to days, with some features lasting up to tens of days and have red-shifted velocities from eighty kilometres per second, all the way down to (and merging with) the circumstellar line, with a few appearing on the blueward side \citep{LagrangeHenri92} with widths from a few up to tens of kilometres per second.
%
The absorption can be described by the transit of evaporating bodies that pass within a few stellar radii of the star, resulting in sublimation of material that produce a large coma containing calcium ions which are then seen as an additional absorption component \citep{Beust91}.
%
Intensive spectroscopic monitoring over several hours show both multiple components transiting the disk of the star \citep{Beust96} and changes of radial velocity of several components are consistent with Keplerian elliptical orbits \citep{Kennedy18} implying at least two \citep{Kiefer14,Pollard24} or more \citep{Heller24} distinct kinematic families of Beta Pictoris exocomets.
%
At least one event is derived with the orbit parallel to the rotational axis of the star \citep{Tobin19}.

From the multiple detections of exocomets in spectroscopy towards \bp{}, the broadband detection of exocomet tails transiting a star were predicted in \citet{1999A&A...343..916L}.
%
A chain of seven exocomets were proposed to explain the shape of one eclipse seen towards KIC~8462852 in \citet{Kiefer17}, and
single exocomet transits were subsequently detected towards the star KIC~3542116 \citep{Rappaport18} with the {\it Kepler} satellite \citep{Borucki10} and in TESS data towards \bp{} \citep{Zieba19}.
%
Observations of \bp{} in subsequent TESS sectors revealed over two dozen transits whose depth follows a power law distribution similar to those of the Solar System \citep{LecavelierdesEtangs22,Pavlenko22}.
%
Automated searches in photometry \citep{Kennedy19} and spectroscopy \citep{BendahanWest24} for additional exocomet systems have been met with limited success.

To the contrary of what is observed in the case of Beta Pictoris exocomets, most molecular and atomic signatures detected in the coma of Solar System comets are emission lines (or bands) instead of absorptions.
%
Spectroscopic observations of Solar System comets when they are very close to the Sun are rare due to observational difficulties.
%
The only comet spectroscopically observed closer than 0.2~au from the Sun is C/1965~S1 Ikeya-Seki.
%
For this comet, it was noticed that the main emission bands or lines detected in its optical spectrum dramatically changed while the comets approached the Sun.
%
At distances greater than 0.4~au, \ce{CH}, \ce{CN}, \ce{C2}, and \ce{C3} emission bands dominated the spectrum.
%
However, at 0.15~au from the Sun, the only molecular emission detected was \ce{CN}, while numerous atomic lines were visible \citep[\ion{[O]}{i}, \ion{Na}{i}, \ion{K}{i}, \ion{Ca}{ii}, \ion{Cr}{i}, \ion{Mn}{i}, \ion{Fe}{i}, \ion{Ni}{i}, \ion{Cu}{i}, \ion{V}{i}; ][]{Dufay65,Thackeray1966,Preston1967,Slaughter1969}.
%
Additionally, a tail of \ion{Fe}{i} atoms was proposed to explain a linear feature imaged in the tail of sungrazing comet C/2016~P1 McNaught 2006P1 \citep{Fulle2007} and \ce{Na} and \ce{K} were detected for comet C/2011 L4 \citep{Fulle13} at 0.46 au.

@@

For the majority of Solar System comets, their optical spectra are dominated by the reflected sunlight from dust grains in their comae, plus molecular and atomic emission lines \citep[e.g. ][]{hyland2019}.
%
Most of the neutral and ionic molecular emission results from resonance fluorescence with solar photons.
%
Some species, such as \ce{H2O+} and \ce{CO+} result from ionization of parent molecules (i.e. molecules released directly by the sublimation of nuclear ices), all other molecules observed at optical wavelengths are second generation species, often created via photodissociation of parent molecules or released by organic-rich grains in the coma.
%
Another process also observed in optical spectrum of comets is prompt atomic emission  ([\ion{O}{i}], [\ion{C}{i}], and [\ion{N}{i}]).
%
Those forbidden transitions are the result of atoms produced in an excited state by the photodissociation of parent molecules in the coma.

Of all cometary gas emission, the highest signal to noise normally occurs with the \ce{CN} (0-0) band at $\lambda\simeq 3880$\AA.
%
It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the comae of comets observed at relatively large distances from the Sun \citep{Bus1991,Fitzsimmons1996}.
%
The relative abundance in the coma of most comets of \ce{OH/CN}$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of approximately 2.6 photons per second per molecule at 1~au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas coma.
%
Historically, the \ce{CN} was believed to be created from photodissociation of \ce{HCN}, which is present in abundances of the order of 1\% relative to water in cometary ices.
%
High-spatial resolution sub-mm mapping of \ce{HCN} distributions supports a nuclear source in some comets \citep{Cordiner2014}.
%
However, it is now known that in many comets a substantial fraction of \ce{CN} is released from sub-micron dust grains in the inner coma of comets \citep[e.g. ][]{Fray2005}.

The \ce{C2} (0-0) band at $\lambda\simeq 5160$\AA{} may be of comparable flux, but has a lower contrast with the underlying dust grain continuum due to its wider bandwidth.
%
The \ce{OH} (0-0) band at $\lambda\simeq 3080$\AA{} generally has higher flux, but unless observed from space the high terrestrial atmospheric absorption severely diminishes the observed flux.
%
Strong \ce{CO+} emission bands have also been observed in a number of comets \citep[the strongest ones are the (3-0) and (2-0) $\mathrm{A^2\Pi-X^2\Sigma}$; ][]{Biver2018}.
%
However this is normally significantly weaker than the observed \ce{CN} emission, with detection in only less than 20 comets.
%
Given the ubiquitous signature of \ce{CN} emission in Solar System comets, we have embarked on an archival search for this species in the exocomets around \bp{}.
%
Detection of this species would provide a solid link between cometary bodies in our Solar System and the \bp{} system.

We detail the observations in Sect.~\ref{sec:data}, along with the correction for the echelle blaze function and normalization of the spectra to a continuum.
%
Our search for \ce{CN} relies on a cross correlation search with a theoretical absorption spectrum for the molecule in Sect.~\ref{sect:CNsearch}, and the discussion and interpretation is in Sect.~\ref{sec:discuss} with our conclusions in Sect.~\ref{sec:conclusion}.

@@

We collated all publicly available HARPS observations of \bp{} obtained between October 2003 and March 2020.
%
Although these observations cover a large baseline, the time between visits varies between 1 day and approximately 2.2 years.
%
Similarly, the number of observations per epoch spans a wide range, between one and 356 exposures, while the exposure times vary between 12 and 900 seconds.
%
This results in an average SNR across order 0 - 10 (order numbers for HARPS will follow the labelling in the fits header -- corresponding to 3780\AA{} and 4075\AA{}) per exposure between 1 and 430, and a nightly SNR between 63 and 2000.
%
To avoid potential edge effects from order merging,  we used the E2DS files downloaded directly from the ESO archive for our analysis.

@@

After all the spectra were all transformed into the stellar rest frame, an average nightly spectrum was made from all spectra within a night for each of the nights of observations. This was done after correcting for variations in the effective blaze profile (for example due to instrumental changes, differential slit or fibre losses, atmospheric absorption, etc.), as outlined below. Note that after this correction, the data still have the overall instrumental blaze-profile included.

@@

The night of 06 May 2018, which has a high signal-to-noise ratio, was chosen to act as an initial estimate for the blaze function.
%
The individual spectra from this night were averaged together to further boost the signal-to-noise ratio.
%
Subsequently, each individual spectrum was divided by this reference spectrum to highlight the changes in the effective profile.
%
This ratio spectrum was subsequently binned using a bin-width of 81 pixels using a robust algorithm to remove outliers within each bin, clipping points more than 2.7 Median Absolute Deviations (MAD) away from the median of each bin.
%
This binned ratio was then fitted using a second order polynomial.
%
The original spectrum was finally divided by this polynomial to correct for the changes.
%
Note that the change of fibre for HARPS in June 2015 (JD$\sim$2,457,180) resulted in an overall change in the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in Sect.~\ref{sect:starcor}.

@@

After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.
%
Each individual spectrum was weighted using the average signal-to-noise ratio provided in the header for orders 0 and 11 (3780\AA{} - 4075\AA{}).

@@

The processing up to this stage removes most of the variations in the effective blaze function, but the overall stellar spectrum and shape of the blaze profile, are still present and need to be removed. 
%
We first perform a second iteration of blaze corrections using a stellar spectrum constructed by averaging the spectra from periods with a low comet activity (see Sect.~\ref{sect:FEBid}), similar to the method before, however, now using a wider binsize of 150 pixels and clipping outliers at 4.5 MAD away from the median.
%
This is done separately pre- and post-fibre change. The correction is done similar to Sect.~\ref{sect:blaze}, however, an 8th order polynomial was used.

After this post-processing the overall (residual) blaze profile and stellar spectrum  needs to be removed.
%
Care must be taken to prevent the removal of (potential) narrow features from the circumstellar disk (as seen in, for example, the \ce{Fe} and \ion{Ca}{II} lines).
%
This is done by combining the nightly spectra without significant cometary activity (see Sect.~\ref{sect:FEBid}) and binning this stacked spectrum in wavelength in bins of 21 pixels.
%
Before binning, the spectrum in each bin was median absolute deviation (MAD) clipped to within $\pm$4.5 MAD of the median of the flux in the bin.
%
The clipped average of the fluxes within each bin was used.
%
Subsequently, the overall spectrum of the star and (residual) blaze was determined by cubic interpolation across the binned points, and divided out of the spectrum for each night.
%
As before, this was done separately pre- and post-fibre change.

@@

After the initial data analysis, we proceed to with our search for lines from \ce{CN}.
%
Although we are interested in lines from the exocomets, we first co-add the data from all the individual epochs, in the stellar rest-frame, to obtain a deep search for circumstellar \ce{CN} absorption.
%
These coadded spectra are shown in Fig.~\ref{fig:spec_CN_stellar_frame}.
%
No obvious feature from the \ce{CN} band jumps out, and we need to combine the signal from the lines within the \ce{CN} band to improve the detection limits.
%
Since the exocomets have a clear radial velocity with respect to \bp{}, and since each exocomet will have its own distinct velocity, we selected the 36 epochs with the strongest exocometary features, a seen in the \ion{Ca}{ii} H line.

@@

The comet features in the \ion{Ca}{ii} H-line ($\lambda=3968$ \AA) were identified after removing the overall stellar line-profile and avoiding the absorption from the circumstellar disk by excluding the central 8 \kms{}.
%
The deepest absorption feature in each observing night was selected, and the location and depth stored.
%
For the comet sample we selected features deeper than 60\% while spectra with features below 15\% were flagged as `low activity'.
%
The distribution of feature locations and depths is shown in Fig.~\ref{fig:FEB_velocity}. The dates, velocities and depths of the selected exocomets can be found in Tab.~\ref{tab:FEB_data}

The spectra for the strong comet sample were coadded, and the combined spectrum for the HARPS data is shown in Fig.~\ref{fig:spec_CN_comet_frame}.
%
As with the circumstellar \ce{CN}, there are no obvious lines from \ce{CN} visible, and we will need to combine multiple lines to improve the signal-to-noise ratio, and see if there is any \ce{CN} present.

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_stellar.pdf}
        \caption{Plot of the stacked spectrum in the stellar restframe (blue) with a CN model for $T=$300~K and N=10$^{14}$\,cm$^{-2}$ overplotted in orange.
        %
        The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_stellar_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/spec_stack_CN_comet.pdf}
        \caption{Similar to Fig.~\ref{fig:spec_CN_stellar_frame} but spectra are stacked in the rest frame of the comet. The large signal around 3860\AA{} is due to the residual from a circumstellar \ion{Fe}{I} line.}
        \label{fig:spec_CN_comet_frame}
        \script{plot_spec_mean.py}
    \end{centering}
\end{figure}

@@

To combine the signal from the many \ce{CN} lines, we cross-correlate the data for each night with a grid of model of \ce{CN}.
%
Cross-sections for \ce{CN} were obtained from ExoMol\footnote{\url{https://www.exomol.com}} \citep{Tennyson12,Tennyson16,Brooke14} with molecular energy levels assumed to be in thermal equilibrium, i.e.\ Boltzmann distributed.
%
We made models for a wide range of temperatures (T$=$\{10, 20, 30, 50, 100, 200, 300, 500, 1000, 2000, 3000\} K) and column densities\footnote{Note that technically, for optically thin lines, this assumes a filling factor $f=1$.
%
Since $f$ is unknown, we actually measure N$f$} (N=\{$10^{11} \ldots 10^{15}$\} cm$^{-2}$.
%
Each of the models was then convolved to include an effective velocity dispersion using a Gaussian for FWHM=\{2.9, 5, 10, 15, 20\} \kms{}.
%
A value of 2.9 \kms{} corresponds approximately to the instrumental resolution of HARPS.
%
The theoretical spectra of \ce{CN} for several different temperatures are shown in Fig.~\ref{fig:CN_theory}.

When creating the CCFs, the region around the narrow, circumstellar \ion{Fe}{I} lines in this wavelength region (see Figs.~\ref{fig:spec_CN_stellar_frame}~and~\ref{fig:spec_CN_comet_frame}) were masked to avoid contamination, especially for the higher temperature CN models.
%
We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm0.35$\AA{} for the \ion{Fe}{I} 3859.9\AA{} line, while for the other lines a width of $\pm0.15$\AA{} was used.
%
Even after cross-correlating, the stacked CCFs (see Fig.~\ref{fig:ccf_mean}) do not show any clear signals, and we therefore proceed to estimate our detection limits.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/HARPS_CN_stellar_frame.pdf}
        \caption{\ce{CN} measurement limits in the stellar rest frame for a \ce{CN} line width of 2.7 \kms{}. Contours show signal-to-noise upper limits.}
        \label{fig:CN_stellar_frame}
        \script{plot_HARPS_CN_stellar_frame.py}
    \end{centering}
\end{figure}
